---
title: "Data Analysis in Software Engineering. Part 2"
output: html_document
header-includes: \usepackage{}
---

This is the R Markdown document for the talk **"Data Analysis for Software Engineering"**, given at the *UCL-Software System Engineering (SSE) Reading Group (RG)* on Wednesday, 12th of August, 2015. This document requires the R system and the Rstudio installed. This document executes all chunks of R code and generates an html document. 

The purpose of the talk is to give a hands-on experience of a data analysis in software engineering. We use basic statistical procedures for analysing some public software engineering datasets. 

#### R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
## Load Data

```{r}
library(foreign)
setwd("/home/javier/DocProjects/PRESI2013/icebergFeb2016")
path2files <- "~/DocProjects/PRESI2013/icebergFeb2016" # Set here the path to the folder where you have downloaded the files
setwd(path2files) #this command sets the default directory
telecom1 <- read.table("Telecom1.csv", sep=",",header=TRUE, stringsAsFactors=FALSE, dec = ".") #read data
size_telecom1 <- telecom1$size
effort_telecom1 <- telecom1$effort

chinaTrain <- read.arff("china3AttSelectedAFPTrain.arff")
china_train_size <- chinaTrain$AFP 
china_train_effort <- chinaTrain$Effort
chinaTest <- read.arff("china3AttSelectedAFPTest.arff")
china_size_test <- chinaTest$AFP
actualEffort <- chinaTest$Effort

```


## Genetic Programming for Symbolic Regression. China dataset.

```{r}
library("rgp")
options(digits = 5)
stepsGenerations <- 1000
initialPopulation <- 500
Steps <- c(1000)
y <- china_train_effort   #
x <- china_train_size  # 

data2 <- data.frame(y, x)  # create a data frame with effort, size
newFuncSet <- mathFunctionSet
# alternatives to mathFunctionSet
# newFuncSet <- expLogFunctionSet # sqrt", "exp", and "ln"
# newFuncSet <- trigonometricFunctionSet
# newFuncSet <- arithmeticFunctionSet
# newFuncSet <- functionSet("+","-","*", "/","sqrt", "log", "exp") # ,, )

gpresult <- symbolicRegression(y ~ x, 
                                data=data2, functionSet=newFuncSet,
                                populationSize=initialPopulation,
                                stopCondition=makeStepsStopCondition(stepsGenerations))

bf <- gpresult$population[[which.min(sapply(gpresult$population, gpresult$fitnessFunction))]]
wf <- gpresult$population[[which.max(sapply(gpresult$population, gpresult$fitnessFunction))]]

bf1 <- gpresult$population[[which.min((gpresult$fitnessValues))]]
plot(x,y)
lines(x, bf(x), type = "l", col="blue", lwd=3)
lines(x,wf(x), type = "l", col="red", lwd=2)

x_test <- china_size_test
estim_by_gp <- bf(x_test)
ae_gp <- abs(actualEffort - estim_by_gp)
mean(ae_gp)

```


## Genetic Programming for Symbolic Regression. Telecom1 dataset.
  - For illustration purposes only. We use all data points. 
```{r}
y <- effort_telecom1   # all data points
x <- size_telecom1   # 

data2 <- data.frame(y, x)  # create a data frame with effort, size
# newFuncSet <- mathFunctionSet
# alternatives to mathFunctionSet
newFuncSet <- expLogFunctionSet # sqrt", "exp", and "ln"
# newFuncSet <- trigonometricFunctionSet
# newFuncSet <- arithmeticFunctionSet
# newFuncSet <- functionSet("+","-","*", "/","sqrt", "log", "exp") # ,, )

gpresult <- symbolicRegression(y ~ x, 
                                data=data2, functionSet=newFuncSet,
                                populationSize=initialPopulation,
                                stopCondition=makeStepsStopCondition(stepsGenerations))

bf <- gpresult$population[[which.min(sapply(gpresult$population, gpresult$fitnessFunction))]]
wf <- gpresult$population[[which.max(sapply(gpresult$population, gpresult$fitnessFunction))]]

bf1 <- gpresult$population[[which.min((gpresult$fitnessValues))]]
plot(x,y)
lines(x, bf(x), type = "l", col="blue", lwd=3)
lines(x,wf(x), type = "l", col="red", lwd=2)

```


